Dynamical Properties of Molecular Cloud Complexes in Galaxies at the Epoch of Reionization

### 2019-03-27 WRITEUP/ms.tex
edits to abstract and first part of intro.  Changed MC to MCC throughout.

\usepackage{xcolor}
\definecolor{apcolor}{HTML}{b3003b}
\definecolor{dlcolor}{HTML}{FF7F00}
\newcommand{\AP}[1]{({\bf \color{apcolor} AP: #1})}
\newcommand{\DL}[1]{({\bf \color{dlcolor} DL: #1})}
\definecolor{afcolor}{HTML}{b3443c}
\newcommand{\AF}[1]{({\bf \color{afcolor} AF: #1})}

@@

\author{T. K. Daisy Leung\altaffilmark{1,2}}
\author{Andrea Pallottini\altaffilmark{3,4}}
\author{Andrea Ferrara\altaffilmark{4,5}}
\author{Mordecai-Mark Mac Low\altaffilmark{2,6,7}}

\affil{\textsuperscript{1} Department of Astronomy, Space Sciences Building, Cornell University, Ithaca, NY 14853, USA; }
\email{tleung@astro.cornell.edu}
\altaffiltext{2}{Center for Computational Astrophysics, Flatiron Institute, 162 Fifth Avenue, New York, NY 10010, USA}
\altaffiltext{3}{Centro Fermi, Museo Storico della Fisica e Centro Studi e Ricerche ``Enrico Fermi'', Piazza del Viminale 1, Roma, 00184, Italy}
\altaffiltext{4}{Scuola Normale Superiore, Piazza dei Cavalieri 7, I-56126 Pisa, Italy}
\altaffiltext{5}{Kavli Institute for the Physics and Mathematics of the Universe (WPI), University of Tokyo, Kashiwa 277-8583, Japan}
\altaffiltext{6}{Institut f{\"u}r Theoretische Astrophysik, Zentrum f{\"u}r Astronomie der Universit{\"a}t Heidelberg, 69120 Heidelberg, Germany}
\altaffiltext{7}{American Museum of Natural History, 79th St.~at Central Park West, New York, NY 10024, USA}

\begin{abstract}
We study the properties of molecular cloud (MC) complexes in a prototypical galaxy (``Alth{\ae}a'') at redshift $z\approx 6$ using cosmological zoom-in simulations.
%
We identify MCs using an H$_2$ density-based clump finder, and compare their mass, size, velocity dispersion, gas surface density, and virial parameter ($\alpha_{\rm vir}$) with those observed in nearby and \z$\lesssim 2$ galaxies.
%
In \flower, MCs masses are in the range $10^{5.5-8.5}$\,\Msun, and have sizes $R\lesssim200$\,pc. Their velocity dispersion and gas surface density are systematically higher than those observed in nearby galaxies, but comparable to starburst galaxies.
%
We identify gravitationally unstable MCs both via an effective, two-component Toomre $Q_{\rm eff}$ parameter (gas+stars), and using a more observationally accessible $\alpha_{\rm vir}$ analysis. We find that MCs in the main disk of \flower are globally stable, but their internal substructures have low $\alpha_{\rm vir}$ and $Q_{\rm eff}$ values, indicative of collapse.
%
%Our results suggest that the more massive and bigger MCs compared to the Milky Way manifest from the
%higher gas mass fraction, surface density, and velocity dispersion.
% , which together sets the scale for fragmentation.
\AF{Abstract is a bit thin. Revise at the end}
High resolution imaging of the first galaxies with the Atacama Large (sub-)Millimeter Array (ALMA) and the Next Generation Very Large Array (ngVLA) can furnish scrutinizing data to test our findings and shed light on \SF since the cosmic dark ages.
\end{abstract}
\keywords{methods: data analysis --
          galaxies: high-redshift --
          galaxies: ISM --
          galaxies: evolution --
          galaxies: formation --
          galaxies: starburst --
          stars: formation}

@@

\section{Introduction}
The growth of galaxies and their subsequent evolution are governed by the baryon cycle --- galaxies accrete gas from the intergalactic medium (IGM) to fuel \SF (and feed their supermassive black holes). Subsequent feedback replenishes and enriches the circumgalactic medium with part of this material. The general consensus is that the growth of \highz galaxies are triggered and supported by massive gas inflows from mergers and/or cosmic web at early cosmic times. Back then, galaxies themselves are more gas-rich and their molecular fraction possibly higher compared to present-day galaxies.

Such massive gas inflows trigger gravitational instabilities which lead to the formation of molecular complexes that are typically more massive ($M_{\rm cl}\approx 10^9$\,\Msun) and extended ($\approx$ sub-kpc) than those observed in nearby galaxies (e.g., \citealt{Gabor13a, Hopkins14a, Inoue16a}).
%
Some theoretical works argue that the migration of such giant massive clumps are largely responsible for the buildup of the bulges of massive galaxies at \z$\sim$\,0 \citep[e.g.,][]{Ceverino10a}.

Given that \highz galaxies statistically represent  the early evolutionary stages of present-day galaxies, studying their ISM properties is essential for understanding how \SF proceeds under more extreme conditions. Current consensus is that early galaxies have higher star formation rates \citep[SFR; ][]{Behroozi13b, Sparre15a, Maiolino15a, Dunlop17a} and smaller sizes \citep[e.g.,][]{Bouwens11a, Ono13a} compared to the local population.
%
As a consequence, we expect them to be significantly more ionized, and have intense and hard interstelar radiation fields (ISRF). Since their metallicity and dust content are also expected to be lower in these early evolutionary stages, shielding of UV photons - responsible for the photoheating of the gas - is strongly reduced. Such differences in turn affect the regulation of the multi-phase ISM thermal and chemical state.

Even in the local Universe, where detailed \obs can be attained, variations in cloud properties have been observed between different galaxy populations (see e.g., \citealt{Hughes10a, Hughes13b}). It is thus intuitive and reasonable to pose the question: {\it what are the physical properties of MCs in early galaxies, and how do they differ from those found in local \galpop?}
%

@@

Earlier epochs still represent an essentially uncharted territory for ISM investigations. At present, it remains unclear how \SF proceeds in the (sub-)$L^*$ galaxy population at \z$\gtrsim$\,6  which is responsible for producing the bulk of the UV photons that reionized the Universe.
%
While ALMA has enabled the detection of \cii158\,$\micron$ and CO line emission in normal (SFR$<$\,100\,\Msun\,yr\pmOne) galaxies at \z$>$\,6 over the past few years \citep[e.g.,][]{Carniani18b, Odorico18a}, the first spatially resolved observations are just starting to become available \citep{Smit18a,Jones17a}.

To answer these questions, isolate key issues, and  accompany ongoing/future experimental efforts, we have undertaken a detailed numerical study whose aim is to characterize the dynamical properties of the star-forming molecular cloud complexes in prototypical (i.e., $L^*$) galaxies in the Epoch of Reionization (EoR).

The paper is structured as follows\footnote{Throughout this paper, we adopt a concordance cosmology, with total matter, vacuum and baryonic densities in units of the critical density $\Omega_{\Lambda}$\eq0.692, $\Omega_m$\eq0.308, $\Omega_b$\eq0.0481, Hubble constant $H_0$\eq100\,$h$\,km s\pmOne\,Mpc\pmOne with $h$\eq0.678, spectral index $n$\eq0.967 and $\sigma_8$\eq0.826 \citep{Planck14a}.}. We start by providing some physical background in \Sec{Back}. In \Sec{sim}, we describe the setup of our simulation and properties of our main galaxy (\flower). In \Sec{eqn}, we describe the method used to identify molecular gas complexes and present the formalism within which we interpret the results. In \Sec{results}, we present the results and the scaling relations for the MCs. We then interpret the results and discuss the implications of our findings in \Sec{diss}, and give our conclusions in \Sec{conclusion}.
%
\section{Physical Background}\label{sec:Back}
We begin by introducing some basic material concerning notable physical ("Larson") relations characterizing MCs, and the gravitational instability of galactic disks, which might be driving MC formation. Such notions will be used in the subsequent analysis of our simulations. 
\subsection{Larson relations and virial parameter}\label{sec:PVE}
\citep{Larson81a} discussed a number of relations among Galactic MC properties, namely the linewidth-size, density-size, and mass-size relations. Larson relations are routinely used for comparing properties of molecular structures in different galactic environments. They also represent a useful framework to analyze our results as they arise from the interplay between gravity and turbulence encoded in the virial theorem.

@@

Summarizing, the virial parameter can be used to quantify the stability/boundedness of an MC. Accounting for the external pressure, a virial parameter of $\alpha_{\rm vir}\lesssim2$ would be unstable \citep{bertoldi:1992}.
%
Such criterion\footnote{In the following, to facilitate comparison with \obs, we derive $\alpha_{\rm vir}$ using the gas component only and ignore contributions due to the stellar component.} is often used in \obs \citep[see e.g., ][]{Kauffmann17b}.

@@

In theoretical and observational works, gravitational instability has been widely discussed in the context of the Toomre $Q$ stability criterion \citep{Toomre64a, Goldreich65b} or its observable proxy  $v_{\rm circ}/\sigma$, i.e., the circular velocity to the disk r.m.s. velocity dispersion \AF{This is not exactly the same $\sigma$ as before} ratio \citep[e.g.,][]{GarciaBurillo03a, Genzel11a, Kassin12a, Leung19a}.
% https://ned.ipac.caltech.edu/level5/March15/Glazebrook/Glazebrook5.html
%
% from linear analysis
For axisymmetric modes, the dispersion relation for the growth of density perturbations in a rotating, turbulent disk of finite thickness $h$ is described by
\begin{equation}
\omega^2 = \kappa^2 - \frac{2\pi G \Sigma |k|}{1 + |k| h} + \sigma^2 k^2\,,
\label{eqn:3Ddisp}
\end{equation}
where $k$ is the wavenumber and $\kappa$ is the epicyclic frequency, defined as:
\begin{equation}
\kappa^2\equiv\frac{2\Omega}{R}\frac{d}{dR}\left(R^2\Omega\right)\,.
\label{eqn:kappa}
\end{equation}
\citep{Romeo92a}.
\AF{$R$ is not the same as the MC radius in the proev. Section}
In Equation~\ref{eqn:3Ddisp} the terms on the r.h.s. are related to rotation, self-gravity and internal pressure, respectively. The Toomre $Q$ parameter for the gas component can be defined as \citep{Toomre64a}:
\begin{equation}
Q_{\rm gas}\equiv\frac{\sigma_{\rm gas}\kappa}{\pi G \Sigma_{\rm gas}}\,.
\label{eqn:Q}
\end{equation}
In the thin disk approximation ($kh\ll1$), instability ($\omega^2 < 0$ in  \Eq{3Ddisp}) occurs on scales $k$ such that $Q < Q_{\rm crit}\simeq1$ (or equivalently $\omega^2 < 0$). Physically, this implies that the local gravitational field 
overcomes support from pressure and rotation, allowing fragmentation and collapse to happen. Similarly, for a collisionless fluid --- as an ensemble of stars --- the Toomre $Q$ parameter is defined by \citep{Toomre64a}:
\begin{equation}
Q_{\star} \equiv\frac{\sigma_{\star}\kappa}{3.36 G \Sigma_{\star}}\,.
\end{equation}

@@

Given \flower's SF stochastic nature, in this work we mostly focus on the analysis of two of its most extreme evolutionary stages (see \Sec{singless}). The two phases correspond to (a) intense accretion (b) starburst (\Fig{SFH}). We are interesting in determining whether MC properties are sensitive to these different dynamical conditions. For completeness, for the other evolutionary stages traced in the simulation we only show scaling relations (see \Fig{alpha16-28}).

@@

\begin{figure*}[htbp]
 \centering
  \includegraphics[scale=0.6]{\figpath/{dual_16_ncut_0.53}.pdf}
  \\ [-2.9em]
  \includegraphics[scale=0.6]{\figpath/{dual_16_ncut_6.81}.pdf}
  \\ [-2.9em]
  \includegraphics[scale=0.6]{\figpath/{dual_16_ncut_18.96}.pdf}
\caption{
Examples of MCs (white contours) identified by the clump-finder in  \flower during its  accreting phase. The color-bar shows the mean H$_2$ number density, weighted by gas mass. Different rows shows the clump-finder results obtained by applying different H$_2$ number density cuts density cuts $(n_{\rm cut})$ as shown by the label. Left and right panels show the galaxy from different viewing angles.
\label{fig:MC}}
\end{figure*}

In \Fig{h2density}, we show the H$_2$ number density ($n_{\rm H2}$) distribution of \flower~in its accreting phase, by including the contribution from the gas within 3.5 kpc from the galaxy center.
%
We note that the distribution is almost flat for $n_{\rm H2}\gtrsim1$\,\cc and it samples the range of densities where clumps are found based on morphological analysis\footnote{For $n_{\rm H2}\gtrsim1$\,\cc the fourth Minkowsky functional of the H$_{2}$ density field is significantly larger than zero. This implies that the field is made of isolated components. See Fig. 6 in \citet{Pallottini17b}.} \citep{Pallottini17b}. We identify MCs by applying 10 equally-spaced volumetric H$_2$ density cuts of ${(n_{\rm cut}/{\rm cm^{-3})}}\eq[0.32, 0.53, 0.88, 1.45, 2.45, 4.08, 5.81, 11.36, 18.96, 31.62]$\footnote{We also tested variations in $n_{\rm cut}$ range and found no qualitative differences (see \Sec{ncut}).} to each snapshot.

To visually appreciate  the clump finding procedure, in \Fig{MC} we overplot the molecular structures identified using a subset of the H$_2$ density cuts ($n_{\rm cut}$\eq0.53, 5.81, and 18.96\,\cc) on the H$_2$ density maps.
Since the molecular structures identified could easily appear as overlapping structures depending on the viewing angle, we also plot them in different three-dimensional projections (right panels of \Fig{MC}) so that one can more easily see that they are collections of disjoint structures.
%
We repeat this identification process for 14 evolutionary stages between redshift \z$\in$[6.0, 7.2], spaced by $\Delta t$\eq50\,Myr.

@@

The mass of an MC is calculated from the uniformly-gridded 3D density field, integrating over the MC volume $V$. The effective size is defined assuming spherical geometry, i.e. $R \equiv (3 V /4 \pi)^{1/3}$.
%
The velocity dispersion of MCs is calculated from non-thermal velocity dispersion ($\sigma_{\rm NT}$) and thermal sound speed ($c_s$):
\begin{equation}
\sigma^2 = \sigma_{\rm NT}^2 + c_s^2.
\label{eqn:veldisp}
\end{equation}
%
In \obs of MC, the linewidths contribution of dense gas contribution is larger then the one from the diffuse gas. We therefore calculate each term on the RHS of Equation~\ref{eqn:veldisp} as a density-weighted quantity. For instance, the non-thermal velocity dispersion is calculated as follows:
\begin{equation}
\sigma_{\rm NT}^2 = \frac{1}{{3}}\frac{\sum_{i} \rho_i \left|\mathbf{v}_i - \mathbf{\bar v}\right|^2}{\sum_i \rho_i}\,,
\end{equation}
where the sum is done for the cells composing each MC.
%
The local sound speed of all identified molecular complexes is much smaller than their turbulent velocities\footnote{Velocity dispersions calculated from velocity field are comparable to those calculated from the pressure field, indicating that contribution from shear is unlikely to dominating the velocity dispersions reported here.\label{ftn:veldisp}}. On average, the Mach number of the MCs is  $\mathcal{M} = \sigma_{\rm NT}/c_s\approx 50$. This is consistent with the global analysis done on \flower by \citet{Vallini18a}.

We show in \Fig{dist} the MC distribution in terms of their molecular gas mass, radius, and gas mass fraction, which we define as
\begin{equation}
f_{\rm gas} = \frac{M_{\rm cl}} {\left(M_{\rm cl} + M_\star\right)},
\end{equation}
where $M_\star$ is the stellar mass within the MC volume.
%
We note that the distributions vary for different evolutionary stages of \flower. The highest density threshold of $n_{\rm cut}$\eq31.62\,\cc yields a minimum MC mass of the order of 10$^{5.5}$\,\Msun for the densest MC.
%
We find $\sim$10$-$13 MCs with masses exceeding 10$^8$\,\Msun across all the evolutionary stages considered in this work, for each  $n_{\rm cut}$ value. \AF{This is true only for low $n_{cut}$? Why in Fig. do you show the valu 18.96 instead?} \DL{MCs w/ Mcl $>$10$^8$\,\Msun is the case for each ncut.} Such massive clouds correspond to the galaxy molecular disk, that is identified as a single component for low $n_{\rm cut}$. The mass of the MCs identified ranges between $M_{\rm cl}\approx$10$^{5.5-8.5}$\,\Msun, consistent with those observed in \z$\sim$2 galaxies in rest-frame UV and optical light \citep{Elmegreen07a, Elmegreen09a}. \AF{you do not comment on $R$ and $f_{gas}$ here..Also, what is the total number of MCs?}

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=\textwidth]{\figpath/minmaxNcut_basicDistributions.pdf}
\caption{Distributions of mass (left), size (middle), and gas mass fraction (right) of MCs identified using the lowest $n_{\rm cut}$ (top panels) and $n_{\rm ncut}$\eq18.96\,\cc (bottom panels).
Note that the scale shown on the y-axes are different between the top and bottom panels, as less MCs are identified at higher $n_{\rm cut}$.
\label{fig:dist}}
\end{figure*}

>>>>

\usepackage{xcolor}
\definecolor{apcolor}{HTML}{b3003b}
\definecolor{dlcolor}{HTML}{FF7F00}
\newcommand{\AP}[1]{({\bf \color{apcolor} AP: #1})}
\newcommand{\DL}[1]{({\bf \color{dlcolor} DL: #1})}
\definecolor{afcolor}{HTML}{b3443c}
\newcommand{\AF}[1]{({\bf \color{afcolor} AF: #1})}
\definecolor{mmcolor}{HTML}{006600}
\newcommand{\MM}[1]{({\bf \color{mmcolor} MM: #1})}

@@

\author{T. K. Daisy Leung\altaffilmark{1,2}}
\author{Andrea Pallottini\altaffilmark{3,4}}
\author{Andrea Ferrara\altaffilmark{4,5}}
\author{Mordecai-Mark Mac Low\altaffilmark{2,6}}

\affil{\textsuperscript{1} Department of Astronomy, Space Sciences Building, Cornell University, Ithaca, NY 14853, USA; }
\email{tleung@astro.cornell.edu}
\altaffiltext{2}{Center for Computational Astrophysics, Flatiron Institute, 162 Fifth Avenue, New York, NY 10010, USA}
\altaffiltext{3}{Centro Fermi, Museo Storico della Fisica e Centro Studi e Ricerche ``Enrico Fermi'', Piazza del Viminale 1, Roma, 00184, Italy}
\altaffiltext{4}{Scuola Normale Superiore, Piazza dei Cavalieri 7, I-56126 Pisa, Italy}
\altaffiltext{5}{Kavli Institute for the Physics and Mathematics of the Universe (WPI), University of Tokyo, Kashiwa 277-8583, Japan}
%mm \altaffiltext{6}{Institut f{\"u}r Theoretische Astrophysik, Zentrum f{\"u}r Astronomie der Universit{\"a}t Heidelberg, 69120 Heidelberg, Germany}
\altaffiltext{6}{American Museum of Natural History, 79th St.~at Central Park West, New York, NY 10024, USA}

\begin{abstract}
%mm rearranged sentence
We study the properties of molecular cloud complexes (MCs) in a cosmological zoom-in simulation of a
prototypical galaxy (``\flower'') at redshift $z\approx 6$.
%
We identify MCs using an H$_2$ density-based clump finder, and compare their mass, size, velocity dispersion, gas surface density, and virial parameter ($\alpha_{\rm vir}$) with those observed in nearby and \z$\lesssim 2$ galaxies.
%
In \flower, MC masses are in the range $10^{5.5-8.5}$\,\Msun, and have sizes $R\lesssim200$\,pc. Their velocity dispersion and gas surface density are systematically higher than those observed in nearby galaxies, but comparable to starburst galaxies.
%
We identify gravitationally unstable MCs both via an effective, two-component Toomre $Q_{\rm eff}$ parameter 
%mm (gas+stars), 
    taking into account both gas and stars, 
and by using a more observationally accessible $\alpha_{\rm vir}$ analysis. We find that MCs in the main disk of \flower are globally stable, but their internal substructures have low $\alpha_{\rm vir}$ and $Q_{\rm eff}$ values, indicative of
%mm
    instability to gravitational 
collapse.
%
%Our results suggest that the more massive and bigger MCs compared to the Milky Way manifest from the
%higher gas mass fraction, surface density, and velocity dispersion.
% , which together sets the scale for fragmentation.
\AF{Abstract is a bit thin. Revise at the end}
High resolution imaging of the first galaxies with the Atacama Large (sub-)Millimeter Array (ALMA) and the Next Generation Very Large Array (ngVLA) can furnish 
%mm scrutinizing 
data to test our findings and shed light on \SF since the cosmic dark ages.
\end{abstract}
\keywords{methods: data analysis --
          galaxies: high-redshift --
          galaxies: ISM --
          galaxies: evolution --
          galaxies: formation --
          galaxies: starburst --
          stars: formation}

@@

\section{Introduction}
The growth of galaxies and their subsequent evolution are governed by the baryon cycle---galaxies accrete gas from the intergalactic medium (IGM) 
%mm to fuel \SF (and feed their  [using "to" implies purpose]
     either directly from the cosmic web, or through mergers with other galaxies.  This gas fuels \SF and feeds central
supermassive black holes. Subsequent feedback replenishes and enriches the circumgalactic medium 
%mm with 
   by expelling some
part of this material. 
%mm [now redundant with first sentence] The general consensus is that the growth of \highz galaxies are triggered and supported by massive gas inflows from mergers and/or the cosmic web at early cosmic times. Back then, 
    Early
galaxies 
%mm themselves 
are more gas-rich and their molecular fraction possibly higher 
%mm compared to
   than
present-day galaxies.

Such massive gas inflows trigger gravitational instabilities that lead to the formation of molecular 
%mm complexes [first use of this term; did you want "cloud complexes" instead of "complexes" for agreement with abstract?] 
   cloud complexes (MCCs)  \MM{changed MC to MCC throughout}
that are typically more massive ($M_{\rm cl}\approx 10^9$\,\Msun) and extended ($\approx$ sub-kpc) than those observed in nearby galaxies (e.g., \citealt{Gabor13a, Hopkins14a, Inoue16a}).
%
Some theoretical works argue that the migration of such giant massive clumps are largely responsible for the buildup of the bulges of massive galaxies at redshift \z$\sim$\,0 \citep[e.g.,][]{Ceverino10a}.

%mm rearranged and combined this and the following paragraph to proceed from observation to conclusion
Early galaxies have higher star formation rates \citep[SFR; ][]{Behroozi13b, Sparre15a, Maiolino15a, Dunlop17a} and smaller sizes \citep[e.g.,][]{Bouwens11a, Ono13a} compared to the local population. 
%
As a consequence, we expect them to be significantly more ionized, and have intense and hard interstelar radiation fields (ISRF). Since their metallicity and dust content are also expected to be lower in these early evolutionary stages, shielding of UV photons---responsible for the photoheating of the gas---  is strongly reduced. Such differences in turn affect the regulation of the thermal and chemical state of the multi-phase interstellar medium (ISM). Studying ISM properties of early galaxies is essential for understanding how \SF proceeds under more extreme conditions.
%
Even in the local Universe, where detailed \obs can be made, variations in 
%mm cloud
     MCC  \MM{do Hughes et al. study cloud complexes, as you do, or can you derive info about complexes from their data?}
properties have been observed between different galaxy populations (see e.g., \citealt{Hughes10a, Hughes13b}).  Given that \highz galaxies statistically represent the early evolutionary stages of present-day galaxies, it is thus reasonable to pose the question: {\it what are the physical properties of MCCs in early galaxies, and how do they differ from those found in local \galpop?}
%

@@

Earlier epochs still represent an essentially uncharted territory for ISM investigations. At present, it remains unclear how \SF proceeds in the (sub-)$L^*$ galaxy population at \z$\gtrsim$\,6  which is responsible for producing the bulk of the UV photons that reionized the Universe.
%
While ALMA has enabled the detection of \cii158\,$\micron$ and CO line emission in normal (SFR$<$\,100\,\Msun\,yr\pmOne) galaxies at \z$>$\,6 over the past few years \citep[e.g.,][]{Carniani18b, Odorico18a}, the first spatially resolved observations are just starting to become available \citep{Jones17a,Smit18a}.

%mm To answer these questions, isolate key issues, and  accompany ongoing/future experimental efforts, 
    To understand the physical properties of MCCs in early galaxies,
we have undertaken a detailed numerical study whose aim is to characterize the dynamical properties of the star-forming %mm molecular cloud complexes
    MCCs
in prototypical (i.e., $L^*$) galaxies in the Epoch of Reionization (EoR).

The paper is structured as follows\footnote{Throughout this paper, we adopt a concordance cosmology, with total matter, vacuum and baryonic densities in units of the critical density $\Omega_{\Lambda}$\eq0.692, $\Omega_m$\eq0.308, $\Omega_b$\eq0.0481, Hubble constant $H_0$\eq100\,$h$\,km s\pmOne\,Mpc\pmOne with $h$\eq0.678, spectral index $n$\eq0.967 and $\sigma_8$\eq0.826 \citep{Planck14a}.}. We start by providing some physical background in \Sec{Back}. In \Sec{sim}, we describe the setup of our simulation and properties of our main galaxy (\flower). In \Sec{eqn}, we describe the method used to identify molecular gas complexes and present the formalism within which we interpret the results. In \Sec{results}, we present the results and the scaling relations for the MCCs. We then interpret the results and discuss the implications of our findings in \Sec{diss}, and give our conclusions in \Sec{conclusion}.
%
\section{Physical Background}\label{sec:Back}
We begin by introducing some basic material concerning notable physical ("Larson") relations characterizing MCCs, and the gravitational instability of galactic disks, which might be driving MCC formation. Such notions will be used in the subsequent analysis of our simulations. 
\subsection{Larson relations and virial parameter}\label{sec:PVE}
\citep{Larson81a} discussed a number of relations among Galactic MCC properties, namely the linewidth-size, density-size, and mass-size relations. Larson relations are routinely used for comparing properties of molecular structures in different galactic environments. They also represent a useful framework to analyze our results as they arise from the interplay between gravity and turbulence encoded in the virial theorem.

@@

Summarizing, the virial parameter can be used to quantify the stability/boundedness of an MCC. Accounting for the external pressure, a virial parameter of $\alpha_{\rm vir}\lesssim2$ would be unstable \citep{bertoldi:1992}.
%
Such criterion\footnote{In the following, to facilitate comparison with \obs, we derive $\alpha_{\rm vir}$ using the gas component only and ignore contributions due to the stellar component.} is often used in \obs \citep[see e.g., ][]{Kauffmann17b}.

@@

In theoretical and observational works, gravitational instability has been widely discussed in the context of the Toomre $Q$ stability criterion \citep{Toomre64a, Goldreich65b} or its observable proxy  $v_{\rm circ}/\sigma$, i.e., the circular velocity to the disk r.m.s. velocity dispersion \AF{This is not exactly the same $\sigma$ as before} ratio \citep[e.g.,][]{GarciaBurillo03a, Genzel11a, Kassin12a, Leung19a}.
% https://ned.ipac.caltech.edu/level5/March15/Glazebrook/Glazebrook5.html
%
% from linear analysis
For axisymmetric modes, the dispersion relation for the growth of density perturbations in a rotating, turbulent disk of finite thickness $h$ is described by
\begin{equation}
\omega^2 = \kappa^2 - \frac{2\pi G \Sigma |k|}{1 + |k| h} + \sigma^2 k^2\,,
\label{eqn:3Ddisp}
\end{equation}
where $k$ is the wavenumber and $\kappa$ is the epicyclic frequency, defined as:
\begin{equation}
\kappa^2\equiv\frac{2\Omega}{R}\frac{d}{dR}\left(R^2\Omega\right)\,.
\label{eqn:kappa}
\end{equation}
\citep{Romeo92a}.
\AF{$R$ is not the same as the MCC radius in the proev. Section}
In Equation~\ref{eqn:3Ddisp} the terms on the r.h.s. are related to rotation, self-gravity and internal pressure, respectively. The Toomre $Q$ parameter for the gas component can be defined as \citep{Toomre64a}:
\begin{equation}
Q_{\rm gas}\equiv\frac{\sigma_{\rm gas}\kappa}{\pi G \Sigma_{\rm gas}}\,.
\label{eqn:Q}
\end{equation}
In the thin disk approximation ($kh\ll1$), instability ($\omega^2 < 0$ in  \Eq{3Ddisp}) occurs on scales $k$ such that $Q < Q_{\rm crit}\simeq1$ (or equivalently $\omega^2 < 0$). Physically, this implies that the local gravitational field 
overcomes support from pressure and rotation, allowing fragmentation and collapse to happen. Similarly, for a collisionless fluid --- as an ensemble of stars --- the Toomre $Q$ parameter is defined by \citep{Toomre64a}:
\begin{equation}
Q_{\star} \equiv\frac{\sigma_{\star}\kappa}{3.36 G \Sigma_{\star}}\,.
\end{equation}

@@

Given \flower's SF stochastic nature, in this work we mostly focus on the analysis of two of its most extreme evolutionary stages (see \Sec{singless}). The two phases correspond to (a) intense accretion (b) starburst (\Fig{SFH}). We are interesting in determining whether MCC properties are sensitive to these different dynamical conditions. For completeness, for the other evolutionary stages traced in the simulation we only show scaling relations (see \Fig{alpha16-28}).

@@

\begin{figure*}[htbp]
 \centering
  \includegraphics[scale=0.6]{\figpath/{dual_16_ncut_0.53}.pdf}
  \\ [-2.9em]
  \includegraphics[scale=0.6]{\figpath/{dual_16_ncut_6.81}.pdf}
  \\ [-2.9em]
  \includegraphics[scale=0.6]{\figpath/{dual_16_ncut_18.96}.pdf}
\caption{
Examples of MCCs (white contours) identified by the clump-finder in  \flower during its  accreting phase. The color-bar shows the mean H$_2$ number density, weighted by gas mass. Different rows shows the clump-finder results obtained by applying different H$_2$ number density cuts density cuts $(n_{\rm cut})$ as shown by the label. Left and right panels show the galaxy from different viewing angles.
\label{fig:MCC}}
\end{figure*}

In \Fig{h2density}, we show the H$_2$ number density ($n_{\rm H2}$) distribution of \flower~in its accreting phase, by including the contribution from the gas within 3.5 kpc from the galaxy center.
%
We note that the distribution is almost flat for $n_{\rm H2}\gtrsim1$\,\cc and it samples the range of densities where clumps are found based on morphological analysis\footnote{For $n_{\rm H2}\gtrsim1$\,\cc the fourth Minkowsky functional of the H$_{2}$ density field is significantly larger than zero. This implies that the field is made of isolated components. See Fig. 6 in \citet{Pallottini17b}.} \citep{Pallottini17b}. We identify MCCs by applying 10 equally-spaced volumetric H$_2$ density cuts of ${(n_{\rm cut}/{\rm cm^{-3})}}\eq[0.32, 0.53, 0.88, 1.45, 2.45, 4.08, 5.81, 11.36, 18.96, 31.62]$\footnote{We also tested variations in $n_{\rm cut}$ range and found no qualitative differences (see \Sec{ncut}).} to each snapshot.

To visually appreciate  the clump finding procedure, in \Fig{MCC} we overplot the molecular structures identified using a subset of the H$_2$ density cuts ($n_{\rm cut}$\eq0.53, 5.81, and 18.96\,\cc) on the H$_2$ density maps.
Since the molecular structures identified could easily appear as overlapping structures depending on the viewing angle, we also plot them in different three-dimensional projections (right panels of \Fig{MCC}) so that one can more easily see that they are collections of disjoint structures.
%
We repeat this identification process for 14 evolutionary stages between redshift \z$\in$[6.0, 7.2], spaced by $\Delta t$\eq50\,Myr.

@@

The mass of an MCC is calculated from the uniformly-gridded 3D density field, integrating over the MCC volume $V$. The effective size is defined assuming spherical geometry, i.e. $R \equiv (3 V /4 \pi)^{1/3}$.
%
The velocity dispersion of MCCs is calculated from non-thermal velocity dispersion ($\sigma_{\rm NT}$) and thermal sound speed ($c_s$):
\begin{equation}
\sigma^2 = \sigma_{\rm NT}^2 + c_s^2.
\label{eqn:veldisp}
\end{equation}
%
In \obs of MCC, the linewidths contribution of dense gas contribution is larger then the one from the diffuse gas. We therefore calculate each term on the RHS of Equation~\ref{eqn:veldisp} as a density-weighted quantity. For instance, the non-thermal velocity dispersion is calculated as follows:
\begin{equation}
\sigma_{\rm NT}^2 = \frac{1}{{3}}\frac{\sum_{i} \rho_i \left|\mathbf{v}_i - \mathbf{\bar v}\right|^2}{\sum_i \rho_i}\,,
\end{equation}
where the sum is done for the cells composing each MCC.
%
The local sound speed of all identified molecular complexes is much smaller than their turbulent velocities\footnote{Velocity dispersions calculated from velocity field are comparable to those calculated from the pressure field, indicating that contribution from shear is unlikely to dominating the velocity dispersions reported here.\label{ftn:veldisp}}. On average, the Mach number of the MCCs is  $\mathcal{M} = \sigma_{\rm NT}/c_s\approx 50$. This is consistent with the global analysis done on \flower by \citet{Vallini18a}.

We show in \Fig{dist} the MCC distribution in terms of their molecular gas mass, radius, and gas mass fraction, which we define as
\begin{equation}
f_{\rm gas} = \frac{M_{\rm cl}} {\left(M_{\rm cl} + M_\star\right)},
\end{equation}
where $M_\star$ is the stellar mass within the MCC volume.
%
We note that the distributions vary for different evolutionary stages of \flower. The highest density threshold of $n_{\rm cut}$\eq31.62\,\cc yields a minimum MCC mass of the order of 10$^{5.5}$\,\Msun for the densest MCC.
%
We find $\sim$10$-$13 MCCs with masses exceeding 10$^8$\,\Msun across all the evolutionary stages considered in this work, for each  $n_{\rm cut}$ value. \AF{This is true only for low $n_{cut}$? Why in Fig. do you show the valu 18.96 instead?} \DL{MCCs w/ Mcl $>$10$^8$\,\Msun is the case for each ncut.} Such massive clouds correspond to the galaxy molecular disk, that is identified as a single component for low $n_{\rm cut}$. The mass of the MCCs identified ranges between $M_{\rm cl}\approx$10$^{5.5-8.5}$\,\Msun, consistent with those observed in \z$\sim$2 galaxies in rest-frame UV and optical light \citep{Elmegreen07a, Elmegreen09a}. \AF{you do not comment on $R$ and $f_{gas}$ here..Also, what is the total number of MCCs?}

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=\textwidth]{\figpath/minmaxNcut_basicDistributions.pdf}
\caption{Distributions of mass (left), size (middle), and gas mass fraction (right) of MCCs identified using the lowest $n_{\rm cut}$ (top panels) and $n_{\rm ncut}$\eq18.96\,\cc (bottom panels).
Note that the scale shown on the y-axes are different between the top and bottom panels, as less MCCs are identified at higher $n_{\rm cut}$.
\label{fig:dist}}
\end{figure*}
